Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-08-15 icse/paper.tex
Clone refactorability

\documentclass[sigconf,review]{acmart}

\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{float}

@@

\subsection{Clone refactorability}
To what extent can found clones be refactored through method extraction, without requiring additional transformations.

>>>>

\documentclass[sigconf,review, table]{acmart}

\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{float}

@@

\subsection{Clone refactorability}
%To what extent can found clones be refactored through method extraction, without requiring additional transformations.
Table \ref{tab:refactorability} shows to what extend clone classes can be refactored by using the ``Extract Method'' refactoring technique. The second column shows our measurements for the complete systems (just like the former experiments). The third column shows our measurements when restricting our search to method bodies. The amount that can be extracted increases because, when restricting our search to method bodies, we do not exclude declarations that can obstruct the possibility of method extraction (for instance a cloned method signature).

\begin{table}[]
\centering
\begin{tabular}{@{}lll@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{All}} & \textit{\textbf{Method Body}} \\ \midrule
Can Be Extracted & 24,157 & 26,109 \\
Is Not A Partial Method & 21,625 & 0 \\
Top-level Node is not a Statement & 19,887 & 4,607 \\
Spans Part of a Block & 12,964 & 13,460 \\
Multiple Return Values & 5,622 & 6,131 \\
Complex Control Flow & 1,106 & 1,216 \\ \bottomrule
\end{tabular}
\caption{Number of clones that can be extracted using the ``Extract Method'' refactoring technique}
\label{tab:refactorability}
\end{table}s
